Invaded vs non invaded

### 2015-10-20 code/08_invaded_vs_non-invaded.Rmd
comparing invaded vs non invaded ecosystems

```{r}
# generate parameter space
space <- expand.grid(type = c("bi", "weight", "AB", "BA"), 
                                         net = 1:length(net)) %>%
    dplyr::inner_join(data.frame(type = c("bi", "AB", "BA", "weight", "weight"),
                                                             keep = c("all", "A", "B", "A", "B")))

@@

driver_nodes <- 1:nrow(space) %>%
    plyr::laply(function(i){
        p <- space[i,]
        net[[p$net]] %>%
            keep_largest_component() %>%
            bipartite_digraph(type = p$type, keep = p$keep) %>%
            n_unmatched_vertex()
    })

@@

Let's look at the number of

>>>>

```{r}
# generate parameter space
space <- expand.grid(type = c("z-bi", "weight", "AB", "BA"), 
                                         net = 1:length(net)) %>%
    dplyr::inner_join(data.frame(type = c("z-bi", "AB", "BA", "weight", "weight"),
                                                             keep = c("all", "A", "B", "A", "B")))

@@

driver_nodes <- 1:nrow(space) %>%
	plyr::laply(function(i){
		p <- space[i,]
		n <- net[[p$net]] %>%
			keep_largest_component() %>%
			bipartite_digraph(type = p$type, keep = p$keep)
		igraph::E(n)$weight <- 1
		n %>%
			n_unmatched_vertex()
	})

@@

Let's look at the number of critical/redundant species

```{r}
node_redundancy %>%
	dplyr::mutate(type = paste(type, keep, sep = ".")) %>%
	dplyr::rename(net_name = net) %>%
	dplyr::group_by(net_name, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	dplyr::group_by() %>%
	dplyr::left_join(space)

```
